---
title: "dplyr_broadway"
author: "Jen Richmond"
date: "15/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
```{r}
library(tidyverse)
library(lubridate)
```

# read data

Tidy Tuesday data week 18 re [Broadway shows](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-04-28/readme.md)
```{r}
grosses <- readr::read_csv(here("data", "broadway.csv"))

```

```{r}
glimpse(grosses) 

```

# 1. lets look at just Hamilton

Make a new dataframe with just Hamilton show weeks. 

```{r}

```

# 2. how have Hamilton ticket prices changed?

Calculate the mean ticket price each month/year since the show started. Visualise changes in ticket price using facet_wrap(~year.)

```{r}

```
# 3. How much money does Hamilton generate on average each week?

How does it compare the Wicked, Rent, and The Lion King? Filter for just those 4 shows.
```{r}

```

Calculate the mean weekly gross by show and year. Plot using facet_wrap(~show). 
```{r}


```

# 4. How many people have seen hamilton since it began?

Add a new column to the hamilton df that sums cumulative audiences and use it to calculate how many people have seen hamilton since it started.   

```{r}

```

# 5. are there other shows that have had as many sell out weeks as hamilton? 

How many weeks has Hamilton had capacity greater or equal to 1?

```{r}

```

What other shows have run for as many (or more) weeks at full capacity? 
```{r}



```


# 6. What proportion of weeks runnnig have the shows run at full capacity?

How many weeks have the 5 shows that have run full for as many (or more weeks) as Hamilton been running for?
```{r}


```

What proportion of weeks have each of the shows run at full capacity? Plot the proportion of weeks at full capacity to see if any show compares to the 100% of Hamilton

```{r}

```

