---
title: "dplyr_broadway"
author: "Jen Richmond"
date: "15/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
```{r}
library(tidyverse)
library(lubridate)
```

# read data

Tidy Tuesday data week 18 re [Broadway shows](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-04-28/readme.md)
```{r}
grosses <- readr::read_csv(here("data", "broadway.csv"))

```

```{r}
glimpse(grosses) 

```

# 1. lets look at just Hamilton

Make a new dataframe with just Hamilton show weeks. 

```{r}
hamilton <- grosses %>%
  filter(show == "Hamilton")
```

# 2. how have Hamilton ticket prices changed?

Calculate the mean ticket price each month/year since the show started. Visualise changes in ticket price using facet_wrap(~year.)

```{r}
tickets <- hamilton %>%
  group_by(month(week_ending, label = TRUE), year(week_ending)) %>%
  summarise(meanticket = mean(avg_ticket_price)) %>%
  rename(month = `month(week_ending, label = TRUE)`, year = `year(week_ending)`)
  
  
tickets %>% ggplot(aes(x = month, 
             y = meanticket, fill = month)) +
  geom_col() +
  facet_wrap(~ year)
```
# 3. How much money does Hamilton generate on average each week?

How does it compare the Wicked, Rent, and The Lion King? Filter for just those 4 shows.
```{r}
fav <- grosses %>%
  filter(show %in% c("Hamilton", "Wicked", "Rent", "The Lion King"))
```

Calculate the mean weekly gross by show and year. Plot using facet_wrap(~show). 
```{r}

options(scipen = 999)

comparison <- fav %>%
  group_by(show, year(week_ending)) %>%
  summarise(meanweeklygross = mean(weekly_gross)) %>%
  rename(year = `year(week_ending)`)
  
  
comparison %>%
    ggplot(aes(x = year,
               y = meanweeklygross)) +
  geom_col() +
  facet_wrap(~show)
```

# 4. How many people have seen hamilton since it began?

Add a new column to the hamilton df that sums cumulative audiences and use it to calculate how many people have seen hamilton since it started.   

```{r}
total <- hamilton %>%
  arrange(week_ending) %>%
  mutate(totalviewers = cumsum(seats_sold)) 


max(total$totalviewers)
```

# 5. are there other shows that have had as many sell out weeks as hamilton? 

How many weeks has Hamilton had capacity greater or equal to 1?

```{r}
hamilton %>%
  count(pct_capacity >= 1)
```

What other shows have run for as many (or more) weeks at full capacity? 
```{r}
fullweeks <- grosses %>%
  group_by(show) %>%
  count(pct_capacity >= 1) %>%
  rename(full = "pct_capacity >= 1") %>%
  filter(full == "TRUE", n >= 241) %>%
  rename(weeks_full = n)


```


# 6. What proportion of weeks runnnig have the shows run at full capacity?

How many weeks have the 5 shows that have run full for as many (or more weeks) as Hamilton been running for?
```{r}
super_shows <- c("Hamilton", "The Book of Mormon", "The Lion King", "The Phantom of the Opera", "Wicked")

runweeks <- grosses %>%
  filter(show %in% super_shows) %>%
  count(show) %>%
  rename(weeks_total = n)

```

What proportion of weeks have each of the shows run at full capacity? Plot the proportion of weeks at full capacity to see if any show compares to the 100% of Hamilton

```{r}
propfull_weeks <- left_join(fullweeks, runweeks) %>%
  mutate(proportion = weeks_full/weeks_total)

propfull_weeks %>%
  ggplot(aes(x = show, y = proportion, fill = show)) +
  geom_col() +
  ggeasy::easy_remove_legend()
```

