---
title: "climbing solution"
author: "Jen Richmond"
date: "15/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages 

```{r}
library(tidyverse)
library(here)
```

# read in the peaks data

This data comes from [Tidy Tuesday Week 39 2020](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-09-22/readme.md)

```{r}

peaks <- read_csv(here("data", "peaks.csv"))

```

# Peaks 

### 1. How many different himalayan peaks are represented in this dataset?

```{r}

n_distinct(peaks$peak_name)
 
```

### 2. what proportion of them have been climbed vs not?

```{r}
peaks %>%
  count(climbing_status) %>%
  pivot_wider(names_from= climbing_status, values_from = n) %>%
  mutate(prop = Climbed/(Climbed + Unclimbed))
```

### 3. is there any difference in the average height of those that have been climbed vs not?

```{r}
peaks %>%
  group_by(climbing_status) %>%
  summarise(meanheight = mean(height_metres))
```

### 4. Which peak was climbed first?

```{r}
peaks %>%
  arrange(first_ascent_year) %>%
  select(first_ascent_year, everything())
```

### 5. How many of the first ascents were achieved by teams from Australia or New Zealand? 

```{r}

peaks %>%
  filter(first_ascent_country %in% c("Australia", "New Zealand")) %>%
  count()

```

### 6. How many of first ascents had teams that involved climbers from NZ or Australia (as well as people from other countries)?

```{r}

peaks %>%
  count(str_detect(first_ascent_country, 'Australia|New Zealand'))
```

### 7. Add a new variable that lists TRUE/FALSE re whether or not there was a Kiwi on the climbing team. Use it to calc what proportion of first ascents had Kiwis on the team?

```{r}

peaks_kiwi <- peaks %>% 
  mutate(kiwi = str_detect(first_ascent_country, 'New Zealand')) 

peaks_kiwi %>%
  filter(climbing_status == "Climbed") %>%
  summarise(sumkiwi = sum(kiwi, na.rm = TRUE), 
            propkiwi = sumkiwi/n())

    
  
```

### 8. How many of the peaks climbed, do we not know the date/country of the ascent?

```{r}
peaks %>%
  group_by(climbing_status) %>%
  count(is.na(first_ascent_year))
 
```

### 9. which peak is closest in height to everest?

```{r}
peaks %>%
  arrange(-height_metres)
```

# 10. What proportion of the  peaks taller than 7000 ft have been climbed? 

```{r}
peaks %>%
  filter(height_metres > 7000) %>%
  count(climbing_status) %>%
  mutate(prop = n / sum(n))
```

